The Importance of Affective States in Privacy Calculus

### 2021-05-03 submission.tex
findings for password section

\section{Discussion}
\subsection{Ad Tracking}
\textbf{TODO}
The inability to rule out the null hypothesis is likely due to the small sample
size of 34 respondents who were asked these questions.

>>>>

\subsection{Password Security}
There exists a strong relationship such that \emph{if an individual used the
same passwords for most of their accounts, they feel worse about it if they use
some password protective measures}. The gamma value of this relationship is
.477, with p<.05 (*). Despite the strength of the relationship, the Chi-Square
p-value of .131 indicates that the null hypothesis cannot be ruled out.

There is a strong positive correlation betwen \emph{how an individual feels when
they reuse an old password, and how they feel if most of their accounts used the
same password}. The gamma correlation value of .733 is significant (p<.001,***).
The null hypothesis can be ruled out (Chi-Square p<.01,**).
\section{Discussion}
\subsection{Ad Tracking}
\textbf{TODO}
The inability to rule out the null hypothesis is likely due to the small sample
size of 34 respondents who were asked these questions.
